Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-02-23 products/manuscript/Manuscript.qmd
Worked on errors preventing us to knit. Mainly fixed the heading

---
title: "Global Distribution of Unintended Pregnancies and Contraceptive Usage"
subtitle: ""
author: Taylor Glass and Aryln Santiago
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../assets/dataanalysis-references.bib
csl: ../assets/apa.csl
---

>>>>

---
title: "Global Distribution of Unintended Pregnancies and Contraceptive Usage"
subtitle: ""
author: Taylor Glass and Aryln Santiago
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---
